### 2015-01-19 src/methodology.Rnw
update
fix javalanche

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. The ABS operator was chosen with
the reasoning that it forces users to consider all parts of the input domain,
and ROR was chosen because it forces users to consider values of predicates.
ROR mutates relational operators, while ABS replaces variables and expressions
by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
PIT are a good map for ROR. Similarly, \Pitin is able to partially provide ABS
functionality.

@@

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.} Mothra supports
three main classes of operators; Replacement (operand) mutators, Expression (operator)
mutators and Statement mutators. The operator selections used in this paper
are groupings of these operators, such as ES, ER, RE, RS, and E.

@@

\subsubsection{Javalanche}
\noindent\textbf{Javalanche \cite{javalanche}.}
Javalanche uses Negate Jump Condition, Omit Method Call, Replace Arithmetic
Operator, and Replace Numerical Constant operators. We have used \Pitnc,
\Pitvmc, \Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.

@@

with $R^2 = 0.96$. This suggests that the variables we should be interested
in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, \Pitri

@@

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested
removal of $n$ most numerous operators. In our experiment, the order of
operators was \Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc,
\Pitcc, \Pitemv, \Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each step and evaluated the effectiveness at each $n$.

>>>>

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al.~\cite{wong1995reducing}.} They selected ROR
and ABS from Mothra for mutation analysis. The ABS operator was chosen with
the reasoning that it forces users to consider all parts of the input domain,
and ROR was chosen because it forces users to consider values of predicates.
ROR mutates relational operators, while ABS replaces variables and expressions
by their positive or negative absolute value or zero. \Pitcb and \Pitnc from
PIT are a good map for ROR. Similarly, \Pitin is able to partially provide ABS
functionality.

@@

\subsubsection{E-Selective}
\noindent\textbf{Offutt et al.~\cite{offutt1996experimental}.} Mothra supports
three main classes of operators; Replacement (operand) mutators, Expression (operator)
mutators and Statement mutators. The operator selections used in this paper
are groupings of these operators, such as ES, ER, RE, RS, and E.

@@

\subsubsection{Javalanche}
\noindent\textbf{Javalanche~\cite{schuler2009efficient,schuler2009javalanche}.}
Javalanche adapts for Java bytecodes the e-selective operator set suggested by
Offutt et al.~\cite{offutt1996experimental} and translated for C by Andrews
et al.~\cite{andrews2005mutation}. The original operators adapted by Andrews
were 1) replacing an integer constant by its predecessor, successor or by a
small constant 2) replacing arithmetic or boolean operators by an operator
of the same class 3) negate boolean conditions in control flow and 4)
statement deletion.

This was adapted to work with bytecodes in Javalanche, and was translated
to~\cite{schuler2009efficient} 1) replace numerical constant
operators 2) replace arithmetic operator, 3) negate jump condition. The last
operator 4) omit method call was added later~\cite{schuler2009javalanche}.
\footnote{
We note that we have already given a translation of the original operators
suggested by Offutt as the idea applies to PIT. Here, we are trying to
evaluate how the translation implemented by Javalanche works.

We also note that while not published, Javalanche has since added
more operators in the default set. However it is not clear if they belong
to a selected set under some criteria or if Javalanche is attempting to
just increase the repertoire of mutations available.}

These map directly to PIT operators \Pitic, \Pitm, \Pitnc, and \Pitvmc.

@@

with $R^2 = 0.96$. This suggests that the variables we should be interested
in are \Pitnvmc, \Pitrc, \Pitdc, \Pitrv, \Pitcc, \Pitemv, \Pitm, and \Pitri.

@@

\subsubsection{N-selection}
\noindent\textbf{Offutt et al.~\cite{offutt1993experimental}.} They suggested
removal of $n$ most numerous operators. In our experiment, the order of
operators was \Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc,
\Pitcc, \Pitemv, \Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin.
We discarded one at each step and evaluated the effectiveness at each $n$.
